StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-07 paper/paper.tex
POPL paper

>>>>

Accuracy-aware transformations~\cite{Zhu:2012:RAP:2103656.2103710} are a class of transformations
that alter a computation according to a set of probabilstic weights and an accuracy
target such that the computation performs more efficiently. StreamReduce uses the subclass
of transformations called \emph{substitution transformations} in worker nodes to adjust
the runtime characteristics of per-datum computation.
